\documentclass{IOS-Book-Article}

% Define \runtitle if not provided by class
\providecommand{\runtitle}[1]{}

\usepackage{mathptmx}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[vietnamese,english]{babel}

% Math and symbols
\usepackage{amsmath,amssymb}
\usepackage{amsthm}
\newtheorem{definition}{Definition}

% Tables and figures
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{float}
\usepackage{enumitem}

% TikZ for diagrams
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows.meta, positioning, fit, backgrounds, calc}

% pgfplots for charts
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}

% Tighten spacing for page limit (no titlesec to avoid cls conflict)
\makeatletter
\renewcommand\section{\@startsection{section}{1}{\z@}%
  {-1.5ex \@plus -0.5ex \@minus -.3ex}%
  {0.8ex \@plus .2ex}%
  {\normalfont\large\bfseries}}
\renewcommand\subsection{\@startsection{subsection}{2}{\z@}%
  {-1.2ex \@plus -0.3ex \@minus -.2ex}%
  {0.5ex \@plus .1ex}%
  {\normalfont\normalsize\bfseries}}
\renewcommand\subsubsection{\@startsection{subsubsection}{3}{\z@}%
  {-1.0ex \@plus -0.2ex \@minus -.2ex}%
  {0.4ex \@plus .1ex}%
  {\normalfont\normalsize\itshape}}
\makeatother
\setlength{\textfloatsep}{8pt plus 2pt minus 2pt}
\setlength{\floatsep}{6pt plus 2pt minus 2pt}
\setlength{\intextsep}{6pt plus 2pt minus 2pt}
\setlength{\abovecaptionskip}{4pt}
\setlength{\belowcaptionskip}{2pt}

\begin{document}

\pagestyle{headings}
\def\thepage{}

\begin{frontmatter}

\title{A Three-Tier Knowledge Graph RAG for Vietnamese Legal Question Answering}

% TODO: Add ORCID iDs for each author
\author[A]{\fnms{Hong Hien} \snm{Le}%
\thanks{Corresponding Author: Le Hong Hien, Faculty of Computer Science, University of Information Technology, Vietnam National University Ho Chi Minh City, Vietnam; E-mail: hienlh.16@grad.uit.edu.vn.}},
\author[A]{\fnms{Dinh Hien} \snm{Nguyen}},
\author[B]{\fnms{Quoc Hung} \snm{Ngo}}
and
\author[A]{\fnms{Viet Dung} \snm{Dang}}

\runningauthor{H.H. Le et al.}
\runtitle{Three-Tier KG RAG for Vietnamese Legal QA}
\address[A]{Faculty of Computer Science, University of Information Technology, Vietnam National University Ho Chi Minh City, Vietnam}
\address[B]{School of Computer Science, University College Dublin, Ireland}

\begin{abstract}
To answer legal questions accurately, a system must navigate hierarchical document structures, follow cross-references, and reason across multiple hops, but standard Retrieval Augmented Generation (RAG) systems cannot do this. Vietnamese legal text makes this gap worse. Tonal language, domain-specific abbreviations, and a rigid structural hierarchy (Law$\to$Chapter$\to$Article$\to$Clause$\to$Point) all compound retrieval difficulty. We propose a three-tier knowledge graph RAG architecture that extends the Legal-Onto Rela-model with a formal knowledge model $\mathcal{M} = (\mathcal{O}, \mathcal{G}, \mathcal{T}, \Phi)$, integrating an OWL ontology for terminological knowledge, a domain-specific knowledge graph for assertional knowledge, and a document tree forest for structural navigation. The three retrieval tiers, specifically LLM-guided tree traversal, dual-level semantic retrieval with intent-aware Personalized PageRank, and Reciprocal Rank Fusion, operate over these representations. Experiments on 375 real Vietnamese legal questions show that our system achieves 75.2\% Hit@10 (MRR 0.545), outperforming BM25 (26.7\%), semantic search (15.8\%), LightRAG (33.9\%), and PageIndex (35.2\%) by substantial margins. Ablation studies confirm each tier's additive contribution, with Tier~3 fusion providing 4.0 percentage points over Tier~1+2 alone. We are not aware of prior work combining ontology-enhanced knowledge graphs with multi-tier retrieval for Vietnamese legal question answering.
\end{abstract}

\begin{keyword}
Knowledge Graph\sep Legal Question Answering\sep Retrieval Augmented Generation\sep Ontology\sep Vietnamese NLP\sep Multi-Tier Retrieval
\end{keyword}

\end{frontmatter}

\section{Introduction}

Every year, millions of queries about business registration, corporate governance, and regulatory compliance appear on Vietnamese legal forums---most receiving incomplete or outdated answers. Automated legal question answering (QA) could help, but the domain imposes retrieval requirements absent from general-purpose QA.

Legal documents exhibit \textbf{complex hierarchical structures}: a single law organizes content into parts, chapters, sections, articles, clauses, and points, where each level carries distinct legal scope. They also contain pervasive \textbf{cross-references}: answering ``Can a foreign investor establish a limited liability company in Vietnam?'' requires following reference chains across multiple articles to assemble conditions, procedures, and exceptions.

The \textbf{Vietnamese legal domain} adds further complexity. Vietnamese is tonal with ambiguous compound word boundaries. Legal practitioners use extensive abbreviations (\textit{HDQT} for ``Hoi dong quan tri'', \textit{CTCP} for ``Cong ty co phan'') that general models miss. Vietnamese law follows a rigid hierarchy such as Constitution, Codes, Decrees, and Circulars, where document type determines legal authority.

Traditional RAG systems \cite{r1} retrieve passages by vector similarity between query and document embeddings \cite{r2}. This works adequately for many domains \cite{r3,r4}, but legal QA exposes its weaknesses. Legal terminology carries precise meanings that general embeddings blur (\textbf{semantic gap}); documents organize content hierarchically, yet vector search treats them as flat text (\textbf{no structural awareness}); and answering a question often requires chaining references across articles---something dense retrieval cannot do (\textbf{no multi-hop reasoning}).

Existing approaches tackle parts of this problem. LightRAG \cite{r5} and GraphRAG \cite{r6} model entity relationships but disregard document hierarchy. PageIndex \cite{r7} exploits structure but has no semantic reasoning component. Legal ontology systems \cite{r8,r9} formalize domain knowledge but remain disconnected from modern retrieval pipelines. We propose a \textbf{three-tier knowledge graph RAG} architecture that brings these capabilities together:
\begin{enumerate}
\item \textbf{LLM-guided tree traversal} through document hierarchies for structural navigation (Tier~1),
\item \textbf{Dual-level semantic retrieval} with intent-aware Personalized PageRank on a domain knowledge graph (Tier~2),
\item \textbf{Reciprocal Rank Fusion} for cross-tier merging with knowledge graph expansion (Tier~3).
\end{enumerate}

We contribute a three-tier RAG architecture that combines structural, semantic, and graph-based retrieval. We also build a Vietnamese legal KG with 1,299 entities (11 types) and 2,577 relations (30 types) using LLM extraction and Vietnamese slug normalization. Our multi-intent PPR algorithm adapts edge weights to query intents. Experiments on 375 real questions show 75.2\% Hit@10 (+41.3pp over the best baseline).

\section{Related Work}
\label{sec:related}

\textbf{RAG and KG-augmented retrieval.}
RAG \cite{r1} grounds generation in retrieved evidence. Since early dense retrieval pipelines \cite{r10}, designs have grown more sophisticated: Self-RAG \cite{r11} adds reflection, CRAG \cite{r12} corrective retrieval, and HyDE \cite{r13} hypothetical document generation; surveys \cite{r3,r4} trace this progression. On the knowledge graph side, GraphRAG \cite{r6} enables multi-hop reasoning and LightRAG \cite{r5} offers lighter entity-relation extraction, but both treat documents as bags of entities and lose structural context. Embedding-based KG methods (TransE \cite{r14}, RotatE \cite{r15}) capture relational patterns yet are limited to single-hop prediction. Personalized PageRank \cite{r16,r17} computes query-specific node importance. PageIndex \cite{r7} takes a different path with LLM-guided tree traversal---achieving high precision with few articles, but missing content outside the traversal path.

\textbf{Legal NLP.}
Legal IR has moved from lexical methods \cite{r18,r19} toward domain-adapted transformers such as LEGAL-BERT \cite{r20}, which capture legal phrasing better than general models but still treat documents as flat passages. Ontology-based approaches \cite{r9} add richer structure; Legal-Onto \cite{r8} combines the Rela-model \cite{r21} with conceptual graphs for Vietnamese Land Law, though it relies on manual inference rules and was not designed for retrieval. For Vietnamese specifically, PhoBERT \cite{r22} and VnCoreNLP \cite{r23} provide foundational NLP capabilities, and Ngo et al.\ \cite{r24} combined BM25 with BERT \cite{r25} and domain heuristics---an effective baseline that nonetheless lacks graph-based reasoning. Surveys \cite{r26,r27} confirm that bridging formal legal knowledge with scalable retrieval remains an open problem.

\textbf{Positioning.}
Table~\ref{tab:related-comparison} maps each system's capabilities. The gap motivating our work is the absence of a system that combines ontological knowledge representation with multi-tier retrieval for Vietnamese legal text.

\begin{table}[H]
\centering\footnotesize
\caption{Feature comparison of legal QA approaches. $^*$Not a RAG system; included for ontology comparison.}
\label{tab:related-comparison}
\resizebox{\columnwidth}{!}{%
\begin{tabular}{llcccccc}
\toprule
\textbf{Category} & \textbf{Feature} & \textbf{NaiveRAG} & \textbf{LightRAG} & \textbf{GraphRAG} & \textbf{PageIndex} & \textbf{Legal-Onto$^*$} & \textbf{Ours} \\
\midrule
\multirow{3}{*}{Retrieval} & Semantic Retrieval & \checkmark & \checkmark & -- & -- & -- & \checkmark \\
& Graph Traversal & -- & \checkmark & \checkmark & -- & -- & \checkmark \\
& Tree Navigation & -- & -- & -- & \checkmark & -- & \checkmark \\
\midrule
\multirow{2}{*}{Knowledge} & Knowledge Graph & -- & \checkmark & \checkmark & -- & \checkmark & \checkmark \\
& Domain Ontology & -- & -- & -- & -- & \checkmark & \checkmark \\
\midrule
\multirow{2}{*}{Reasoning} & Multi-hop & -- & -- & \checkmark & -- & \checkmark & \checkmark \\
& Intent-aware & -- & -- & -- & -- & -- & \checkmark \\
\midrule
\multirow{2}{*}{Integration} & Multi-tier & -- & -- & -- & -- & -- & \checkmark \\
& Rank Fusion & -- & -- & -- & -- & -- & \checkmark \\
\bottomrule
\end{tabular}}%
\end{table}

\section{Methodology}
\label{sec:method}

\subsection{Problem Formulation}

Given a legal corpus $\mathcal{D} = \{d_1, \ldots, d_m\}$ with hierarchically organized articles and a query $q$, retrieve a ranked list $A^* = [a_1^*, \ldots, a_k^*]$ of relevant articles. We define $A^* = \Phi(q, \mathcal{M})$ where $\mathcal{M} = (\mathcal{O}, \mathcal{G}, \mathcal{T}, \Phi)$ integrates ontology $\mathcal{O}$ (terminological), knowledge graph $\mathcal{G}$ (assertional), document forest $\mathcal{T}$ (structural), and retrieval functions $\Phi$.

\subsection{System Overview}

Figure~\ref{fig:architecture} illustrates the architecture. The \textbf{offline phase} constructs $\mathcal{M}$ through parsing, extraction, and ontology generation. The \textbf{online phase} processes queries via ontology expansion (Stage~0) followed by three retrieval tiers leveraging $\mathcal{T}$, $\mathcal{G}$, and $\mathcal{O}$.

% Figure 1: System Architecture
\begin{figure}[H]
\centering
\resizebox{0.85\textwidth}{!}{%
\begin{tikzpicture}[
    % Styles
    box/.style={rectangle, draw, rounded corners, minimum height=0.7cm, minimum width=1.8cm, align=center, font=\small},
    phase/.style={rectangle, draw, dashed, rounded corners, inner sep=8pt},
    tier/.style={rectangle, draw, dashed, rounded corners, inner sep=6pt, fill=blue!3},
    arrow/.style={-{Stealth[length=2mm]}, thick},
    dataarrow/.style={-{Stealth[length=2mm]}, thick, blue!60},
    label/.style={font=\footnotesize\bfseries},
]

% === OFFLINE PHASE (Left) ===
\node[box, fill=orange!20] (doc) at (0,0) {Legal\\Document};
\node[box, fill=blue!15] (parse) at (3,0) {Document\\Parsing};
\node[box, fill=blue!15] (extract) at (6,0) {LLM Entity \&\\Relation Extraction};
\node[box, fill=green!15] (kgbuild) at (3,-2.5) {Incremental KG\\Builder (Dedup)};
\node[box, fill=green!15] (summary) at (6,-2.5) {Chapter \&\\Article Summaries};
\node[box, fill=purple!20, minimum width=3cm] (kg) at (4.5,-5) {Knowledge Model $\mathcal{M}$\\$(\mathcal{O}, \mathcal{G}, \mathcal{T}, \Phi)$};

% Offline arrows
\draw[arrow] (doc) -- (parse);
\draw[arrow] (parse) -- (extract);
\draw[arrow] (extract.south) -- ++(0,-0.5) -| (kgbuild.north);
\draw[arrow] (extract.south) -- ++(0,-0.5) -| (summary.north);
\draw[arrow] (kgbuild.south) -- (kg.north west);
\draw[arrow] (summary.south) -- (kg.north east);

% Offline phase box
\begin{scope}[on background layer]
\node[phase, fill=gray!5, fit=(doc)(parse)(extract)(kgbuild)(summary)(kg), label={[label]above:Offline Phase: Knowledge Model Construction}] (offline) {};
\end{scope}

% === ONLINE PHASE (Right) ===
\node[box, fill=yellow!20] (query) at (10.5,0) {User\\Query};
\node[box, fill=blue!15] (analyzer) at (13.5,0) {Query Analyzer\\(Intent + Type)};

% Tier 1
\node[box, fill=green!15] (tree) at (11,-2.5) {Tree Traversal\\(LLM-guided)};

% Tier 2
\node[box, fill=green!15] (dual) at (16,-2.5) {Dual-Level\\Retriever};
\node[box, fill=green!15] (ppr) at (16,-4.0) {Intent-Aware\\PPR};

% Tier 3
\node[box, fill=red!15] (bridge) at (13.5,-5.8) {Semantic Bridge\\(RRF Fusion)};

% Output
\node[box, fill=purple!20] (gen) at (13.5,-7.5) {Answer\\Generation};
\node[box, fill=yellow!20] (answer) at (16.5,-7.5) {Legal\\Answer};

% Online arrows
\draw[arrow] (query) -- (analyzer);
\draw[arrow] (analyzer.south) -- ++(0,-0.5) -| (tree.north);
\draw[arrow] (analyzer.south) -- ++(0,-0.5) -| (dual.north);
\draw[arrow] (dual) -- (ppr);
\draw[arrow] (tree.south) |- (bridge.west);
\draw[arrow] (ppr.south) |- (bridge.east);
\draw[arrow] (bridge) -- (gen);
\draw[arrow] (gen) -- (answer);

% KG to Online connections
\coordinate (splitpt) at (8.5,-5);
\draw[blue!60, thick] (kg.east) -- (splitpt);
\draw[blue!60, thick] (splitpt) -- (8.5,-2.5);
\draw[dataarrow] (8.5,-2.5) -- (tree.west);
\draw[dataarrow] (splitpt) -- (8.5,-5.8) -- (bridge.west);

% Tier labels
\node[font=\scriptsize\itshape, gray, anchor=west] at (12.1,-2.5) {Tier 1};
\node[font=\scriptsize\itshape, gray, anchor=east] at (14.9,-2.5) {Tier 2};
\node[font=\scriptsize\itshape, gray] at (13.5,-5.1) {Tier 3};

% Online phase box
\begin{scope}[on background layer]
\node[phase, fill=gray!5, fit=(query)(analyzer)(tree)(dual)(ppr)(bridge)(gen)(answer), label={[label]above:Online Phase: Three-Tier Query Processing}] (online) {};
\end{scope}

\end{tikzpicture}
}
\caption{System architecture. Offline: knowledge model construction. Online: three-tier query processing (Tier~1: tree traversal, Tier~2: semantic+PPR, Tier~3: RRF fusion).}
\label{fig:architecture}
\end{figure}

\subsection{Knowledge Representation Model}

Our model extends Legal-Onto \cite{r8}, which defines $K = (C, R, \textit{RULES}) + (\textit{Key}, \textit{Rel}, \textit{weight})$ integrating the Rela-model \cite{r21} with conceptual graphs. We extend this by separating terminological from assertional knowledge, adding structural representation, and replacing manual rules with LLM-based retrieval.

\begin{definition}[Legal Knowledge Model]
Given a legal corpus $\mathcal{D}$, the knowledge model is:
\begin{equation}
\mathcal{M} = (\mathcal{O}, \mathcal{G}, \mathcal{T}, \Phi)
\end{equation}
where $\mathcal{O}$ is a domain ontology, $\mathcal{G}$ is a knowledge graph, $\mathcal{T}$ is a document forest, and $\Phi$ is a set of retrieval functions.
\end{definition}

\textbf{Ontology} $\mathcal{O} = (C, P, H, L)$ represents terminological knowledge: $C$~=~OWL classes for legal entity types, $P = P_\text{obj} \cup P_\text{data}$~=~object and datatype properties, $H \subseteq C \times C$~=~class hierarchy via \texttt{rdfs:subClassOf} (4-level taxonomy), and $L: C \cup P \to \text{Vietnamese}$~=~label mapping (e.g., \texttt{JointStockCompany} $\mapsto$ ``cong ty co phan''). This separates the TBox from Legal-Onto's flat concept set, enabling class hierarchy traversal for query expansion.

\textbf{Knowledge Graph} $\mathcal{G} = (E, R)$ represents assertional knowledge. Each entity $e = (\textit{id}, \textit{name}, \textit{type}, \textit{conf}, \textit{src})$ has a slug-normalized ID, one of 11 types (Organization, Person/Role, Legal Term, Legal Reference, Condition, Action, Penalty, etc.), confidence score, and source provenance. Each relation $r = (e_i, \textit{pred}, e_j, \textit{evid}, \textit{conf})$ carries evidence text and confidence across 30 types with formal properties: symmetric $\{\textit{related\_to}, \textit{contradicts}, \textit{synonym}\}$ and transitive $\{\textit{is\_a}, \textit{part\_of}, \textit{contains}\}$. Compared to Legal-Onto's conceptual graph with binary similarity vectors, $\mathcal{G}$ provides richer typing, confidence tracking, and evidence-backed relations.

\textbf{Document Forest} $\mathcal{T} = \{T_1, \ldots, T_m\} \cup X$ represents structural knowledge. Each $T_i$ is a rooted tree with six levels (Document${}\to{}$\allowbreak Chapter${}\to{}$\allowbreak Section${}\to{}$\allowbreak Article${}\to{}$\allowbreak Clause${}\to{}$\allowbreak Point), and $X$ contains cross-reference edges between documents. This component, absent from Legal-Onto, enables Tier~1's structural traversal.

\textbf{Retrieval Functions} $\Phi = \{\phi_0, \phi_1, \phi_2, \phi_3\}$ replace Legal-Onto's manual inference rules:
\begin{itemize}[nosep,leftmargin=1.5em]
\item $\phi_0\colon Q \times \mathcal{O} \to Q'$ (ontology expansion),
\item $\phi_1\colon Q' \times \mathcal{T} \to 2^A$ (tree traversal),
\item $\phi_2\colon Q' \times \mathcal{G} \times \mathcal{O} \to 2^A$ (semantic retrieval),
\item $\phi_3\colon 2^A \times 2^A \times \mathcal{G} \to A^*$ (fusion).
\end{itemize}
Where Legal-Onto applies hand-crafted deductive rules, our functions leverage LLM reasoning while preserving formal relation properties in the graph structure.

\subsection{Knowledge Graph Construction}

The offline phase builds $\mathcal{G}$ through four steps. \textbf{(1)~Document Parsing:} Legal documents are parsed into hierarchical trees following Vietnamese formatting standards, forming the document forest $\mathcal{T}$ with position, parent-child relationships, and cross-references. \textbf{(2)~Entity-Relation Extraction:} A single LLM call per article extracts entities (11 types) and relations simultaneously, producing evidence-grounded triples with source citations. \textbf{(3)~Incremental KG Building:} Entities are deduplicated via Vietnamese slug normalization: Unicode NFD decomposition, diacritics removal, and lowercasing (e.g., ``Cong ty co phan'' $\to$ \textit{cong-ty-co-phan}), which uses a 4-pass pipeline: exact cache lookup, synonym matching (17 entries), abbreviation expansion (25 entries), and new slug creation. \textbf{(4)~Summary Generation:} LLM-generated chapter and article summaries enable Tier~1's tree traversal decisions.

\subsubsection{Intent-Aware Edge Weights}

Table~\ref{tab:intent-weights} defines intent-specific weight multipliers for PPR.

\begin{table}[H]
\centering\footnotesize
\caption{Intent-relation weight matrix.}
\label{tab:intent-weights}
\begin{tabular}{lccccc}
\toprule
\textbf{Relation} & \textbf{Definition} & \textbf{Procedure} & \textbf{Right} & \textbf{Obligation} & \textbf{Penalty} \\
\midrule
defines\_as & 1.0 & 0.5 & 0.5 & 0.5 & 0.5 \\
includes & 0.95 & 0.5 & 0.5 & 0.5 & 0.5 \\
requires & 0.5 & 1.0 & 0.5 & 0.85 & 0.5 \\
has\_authority & 0.5 & 0.5 & 1.0 & 0.5 & 0.5 \\
has\_obligation & 0.5 & 0.5 & 0.5 & 1.0 & 0.5 \\
has\_penalty & 0.5 & 0.5 & 0.5 & 0.5 & 1.0 \\
\bottomrule
\end{tabular}
\end{table}

This allows PPR to traverse paths most relevant to query intent (e.g., \textit{defines\_as} for definitions, \textit{requires} for procedures).

\subsection{Three-Tier Retrieval}

\subsubsection{Stage 0: Query Analysis}

The query analyzer performs: (1)~\textbf{intent detection} across 6 types (Penalty, Definition, Procedure, Requirement, Reference, General) via Vietnamese regex with LLM fallback; (2)~\textbf{type classification} into 7 categories; (3)~\textbf{abbreviation expansion} (e.g., \textit{TNHH} $\to$ \textit{trach nhiem huu han}); and (4)~\textbf{ontology expansion} $\phi_0(q, \mathcal{O})$ via class hierarchy traversal in $H$ with Vietnamese label lookup through $L$.

\subsubsection{Tier 1: LLM-Guided Tree Traversal}

Tier~1 navigates $\mathcal{T}$ using LLM reasoning in three loops: \textbf{Loop~0} (Forest$\to$Document) selects top~3 documents; \textbf{Loop~1} (Document$\to$Chapter) selects top~6 chapters using summaries and keywords; \textbf{Loop~2} (Chapter$\to$Article) identifies top~7 articles from article summaries. General Provisions chapters are automatically included. Each loop produces a reasoning path for interpretable retrieval.

\subsubsection{Tier 2: Dual-Level Semantic Retrieval}

Tier~2 performs hybrid semantic search over $\mathcal{G}$ and $\mathcal{O}$ with six components. \textit{Low-level} (entity-specific): (1)~keyphrase matching, (2)~query-entity cosine similarity, (3)~intent-aware PPR, (4)~ontology class matching. \textit{High-level} (theme/concept): (5)~legal theme identification, (6)~hierarchy traversal through $\mathcal{O}$'s taxonomy. The combined score is:
\begin{equation}
S_{\text{T2}} = .05 S_{\text{kp}} + .20 S_{\text{con}} + .25 S_{\text{PPR}} + .20 S_{\text{sem}} + .15 S_{\text{thm}} + .15 S_{\text{hier}}
\end{equation}

\textbf{Multi-Intent Personalized PageRank.} The PPR component computes query-specific node importance on $\mathcal{G}$:
\begin{equation}
\text{PPR}(v) = (1-\alpha) \sum_{u \in N(v)} \frac{w(u,v) \cdot \text{PPR}(u)}{d(u)} + \alpha \cdot p(v)
\end{equation}
where $\alpha=0.15$ is the teleport probability, $w(u,v)$ is the edge weight adjusted by query intent (Table~\ref{tab:intent-weights}), $d(u)$ is the weighted out-degree of $u$, and $p(v)$ is the personalization vector seeded from matched entities.

\subsubsection{Tier 3: Semantic Bridge (RRF Fusion)}

Tier~3 merges results from Tier~1 and Tier~2 using Reciprocal Rank Fusion \cite{r28}:
\begin{equation}
\text{RRF}(d) = \sum_{s \in \{T1, T2, KG\}} w_s \cdot \frac{1}{k + \text{rank}_s(d)}
\end{equation}
where $k=60$ and source weights are $w_{T1}=0.8$, $w_{T2}=1.0$, $w_{KG}=1.2$. RRF handles heterogeneous score distributions (LLM discrete selections vs.\ continuous semantic scores) without calibration.

\textbf{Adjacent article expansion.} After RRF scoring, we expand $\pm 2$ articles from each result with decay factor 0.7, as correct answers often lie within $\pm 3$ articles. Top-ranked articles are passed to an LLM for answer generation.

\section{Experiments}
\label{sec:experiments}

\subsection{Experimental Setup}

\textbf{Dataset.} We evaluate on Vietnam Enterprise Law 2020 (No.~59/2020/QH14) and 9 related decrees (10 chapters, 218 articles). The evaluation set: 375 real questions from Vietnamese legal platforms (LuatVietnam, ThuVienPhapLuat), expert-annotated (1--8 relevant articles per question, avg.\ 2.3). Categories: Article lookup (41.6\%), Guidance document (26.1\%), Situation analysis (20.0\%), Compare regulations (8.5\%), Case law lookup (3.8\%).

\textbf{Knowledge graph statistics.} Table~\ref{tab:kg-stats} summarizes the constructed knowledge graph.

\begin{table}[H]
\centering\footnotesize
\caption{Knowledge graph statistics.}
\label{tab:kg-stats}
\begin{tabular}{lr@{\hskip 1.2cm}lr@{\hskip 1.2cm}lr}
\toprule
\textbf{Entity Type} & \textbf{Count} & \textbf{Relation Type} & \textbf{Count} & \textbf{Structure} & \textbf{Count} \\
\midrule
Total Entities & 1,299 & Total Relations & 2,577 & Document Tree Nodes & 1,847 \\
Organization & 187 & requires & 423 & Chapter Summaries & 10 \\
Person/Role & 156 & has\_authority & 312 & Article Summaries & 218 \\
Legal Term & 234 & applies\_to & 287 & & \\
Legal Reference & 198 & references & 265 & & \\
Condition & 178 & includes & 234 & & \\
Action & 163 & defines\_as & 198 & & \\
Other types & 183 & Other relations & 858 & & \\
\bottomrule
\end{tabular}
\end{table}

\textbf{Implementation.} Claude~3.5 Haiku for tree traversal and query analysis; Gemini~2.0 Flash for entity extraction. Embeddings: \texttt{paraphrase-multilingual-MiniLM-L12-v2} \cite{r2}. PPR: iterative computation, max~50 iterations, tolerance~$10^{-6}$. All LLM responses cached in SQLite ($\sim$1.1\,GB) for reproducibility.

\textbf{Metrics.} Hit@$k$, Recall@$k$, Precision@$k$, NDCG@$k$ at $k \in \{1,3,5,10,20,30,50\}$, and MRR.

\subsection{Baselines}

\textbf{BM25} \cite{r18} ($k_1\!=\!1.2$, $b\!=\!0.75$); \textbf{TF-IDF} \cite{r19} with Vietnamese segmentation; \textbf{Semantic Search} \cite{r2} using multilingual sentence-transformers; \textbf{LightRAG} \cite{r5} with default parameters; \textbf{PageIndex} \cite{r7} (our Tier~1 in isolation).

\subsection{Main Results}

Table~\ref{tab:main-results} presents Hit@$k$ performance.

\begin{table}[H]
\centering\footnotesize
\caption{Hit@$k$ performance (\%). Best \textbf{bold}, 2nd \underline{underlined}.}
\label{tab:main-results}
\begin{tabular}{l@{\hskip 3pt}r@{\hskip 3pt}r@{\hskip 3pt}r@{\hskip 3pt}r@{\hskip 3pt}r@{\hskip 3pt}r}
\toprule
\textbf{Method} & \textbf{Hit@5} & \textbf{Hit@10} & \textbf{Hit@20} & \textbf{Hit@30} & \textbf{Hit@50} & \textbf{Avg.~Articles} \\
\midrule
Semantic & 7.4 & 15.8 & 38.5 & 44.3 & 48.3 & 50.0 \\
BM25 & 15.0 & 26.7 & 50.1 & 58.1 & 79.2 & 50.0 \\
TF-IDF & 15.8 & 28.8 & 50.7 & 62.0 & \underline{82.3} & 50.0 \\
LightRAG & 18.8 & 33.9 & \underline{51.0} & \underline{66.2} & 70.3 & 32.8 \\
PageIndex & \underline{31.7} & \underline{35.2} & 35.2 & 35.2 & 35.2 & 3.9 \\
\textbf{3-Tier (ours)} & \textbf{68.5} & \textbf{75.2} & \textbf{82.1} & \textbf{84.0} & \textbf{86.4} & 52.3 \\
\bottomrule
\end{tabular}
\end{table}

Semantic search scores only 15.8\% Hit@10 due to general embeddings failing on Vietnamese legal semantics. BM25/TF-IDF achieve moderate performance ($\sim$27--29\%) with weak ranking. LightRAG improves to 33.9\% through entity-relation modeling but lacks legal precision. PageIndex achieves 35.2\% with only 3.9 articles, demonstrating targeted but limited retrieval. Our 3-Tier system reaches 75.2\% (+41.3pp over the best baseline).

Figure~\ref{fig:hitk-comparison} visualizes the consistent advantage across all $k$ values.

\begin{figure}[H]
\centering
\begin{tikzpicture}
\begin{axis}[
    width=\columnwidth,
    height=4cm,
    ybar,
    bar width=2.8pt,
    ylabel={Hit Rate (\%)},
    symbolic x coords={@5,@10,@20,@30,@50},
    xtick=data,
    ymin=0, ymax=100,
    enlarge x limits=0.15,
    legend style={at={(0.5,-0.3)}, anchor=north, legend columns=3, font=\scriptsize},
    every axis plot/.append style={fill opacity=0.85},
    grid=major,
    grid style={dashed, gray!30},
]
\addplot[fill=gray!40, draw=gray!60] coordinates {(@5,7.4) (@10,15.8) (@20,38.5) (@30,44.3) (@50,48.3)};
\addplot[fill=blue!30, draw=blue!50] coordinates {(@5,15.0) (@10,26.7) (@20,50.1) (@30,58.1) (@50,79.2)};
\addplot[fill=cyan!30, draw=cyan!50] coordinates {(@5,15.8) (@10,28.8) (@20,50.7) (@30,62.0) (@50,82.3)};
\addplot[fill=orange!40, draw=orange!60] coordinates {(@5,18.8) (@10,33.9) (@20,51.0) (@30,66.2) (@50,70.3)};
\addplot[fill=purple!30, draw=purple!50] coordinates {(@5,31.7) (@10,35.2) (@20,35.2) (@30,35.2) (@50,35.2)};
\addplot[fill=red!50, draw=red!70] coordinates {(@5,68.5) (@10,75.2) (@20,82.1) (@30,84.0) (@50,86.4)};
\legend{Semantic, BM25, TF-IDF, LightRAG, PageIndex, 3-Tier (ours)}
\end{axis}
\end{tikzpicture}
\caption{Hit@$k$ comparison across all methods.}
\label{fig:hitk-comparison}
\end{figure}

\subsection{Detailed IR Metrics}

Table~\ref{tab:detailed-metrics} reports detailed metrics. MRR is 0.545 (first relevant article at avg.\ rank~$\sim$1.8). Recall reaches 67.4\% at $k\!=\!50$.

\begin{table}[H]
\centering\footnotesize
\caption{Detailed IR metrics for 3-Tier system.}
\label{tab:detailed-metrics}
\begin{tabular}{lrrrr}
\toprule
\textbf{$k$} & \textbf{Hit} & \textbf{Recall} & \textbf{Precision} & \textbf{NDCG} \\
\midrule
1 & 42.7 & 23.9 & 42.7 & 42.7 \\
5 & 68.5 & 46.7 & 18.3 & 43.4 \\
10 & 75.2 & 51.8 & 10.3 & 45.4 \\
20 & 82.1 & 59.2 & 6.1 & 47.8 \\
50 & 86.4 & 67.4 & 2.9 & 49.9 \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Ablation Study}

Table~\ref{tab:ablation} isolates each tier's contribution.

\begin{table}[H]
\centering\footnotesize
\caption{Ablation study: per-tier contribution (\%).}
\label{tab:ablation}
\begin{tabular}{lr}
\toprule
\textbf{Configuration} & \textbf{Hit@10} \\
\midrule
Tier 1 only (Tree Traversal) & 56.2 \\
Tier 2 only (DualLevel + PPR) & 61.7 \\
Tier 1 + Tier 2 (no RRF fusion) & 71.2 \\
Full 3-Tier (with Tier 3 RRF) & \textbf{75.2} \\
\bottomrule
\end{tabular}
\end{table}

Each tier adds value: Tier~1 alone 56.2\%, +Tier~2 yields 71.2\% (+15.0pp), +Tier~3 reaches 75.2\% (+4.0pp). Among hits, 70\% originate from Tier~1 while Tier~2 adds 14\% unique hits, confirming complementarity.

\subsection{Analysis}

\subsubsection{Performance by Query Type}

Table~\ref{tab:category-results} breaks down Hit@10 by question category.

\begin{table}[H]
\centering\footnotesize
\caption{Hit@10 by question category (\%).}
\label{tab:category-results}
\begin{tabular}{lrr}
\toprule
\textbf{Category} & \textbf{Hit@10} & \textbf{Count} \\
\midrule
Article lookup & 82.1 & 156 \\
Guidance document & 73.5 & 98 \\
Situation analysis & 71.3 & 75 \\
Compare regulations & 68.8 & 32 \\
Case law lookup & 61.1 & 18 \\
\bottomrule
\end{tabular}
\end{table}

Article lookup (82.1\%) benefits most from Tier~1's structured navigation. Complex categories benefit from Tier~2's multi-hop KG reasoning.

\subsubsection{Qualitative and Error Analysis}

\textbf{Success:} ``Conditions for establishing a joint-stock company?'' (Tier~1 navigates to Articles~111--112; Tier~2 adds Article~17 via \textit{requires}; Tier~3 fuses to rank all three in top~3, achieving \textbf{Hit@3}).
\textbf{Failure:} ``Penalty for late annual report?'' (the penalty resides in Decree~122/2021, a separate document; Tier~2's KG partially reaches it but ranks at position~15).

We manually categorized the 93 failed queries (24.8\%). The dominant cause is \textbf{cross-document gaps} (39 queries, 41.9\%): the answer resides in a decree not linked to the main law's KG. \textbf{Compound term splitting} accounts for 26 failures (28.0\%): Vietnamese word segmentation fragments multi-syllable legal terms, degrading both embedding quality and entity matching. The remaining 28 failures (30.1\%) stem from \textbf{ambiguous intent}: queries mixing multiple intent types cause PPR to favor one traversal path over another.

% Walkthrough figure removed for space; the success/failure cases above illustrate the three-tier process.

\textbf{Reproducibility.} All LLM responses are cached in SQLite ($\sim$1.1\,GB), making results deterministic (std.\ dev.\ = 0).

\section{Discussion}
\label{sec:discussion}

The ablation results (Table~\ref{tab:ablation}) show that the tiers are genuinely complementary rather than redundant. Tier~1 accounts for 70\% of hits through structural navigation, while Tier~2 contributes 14\% of hits that Tier~1 misses entirely---typically articles reachable only via cross-references or thematic relations. The 15pp gain from combining them confirms they target different failure modes.

Intent-aware PPR proves particularly effective for situation analysis and guidance queries. By weighting edges according to query intent (Table~\ref{tab:intent-weights}), the algorithm surfaces paths that generic graph traversal would rank lower---a ``procedure'' query and a ``penalty'' query about the same entity need different neighborhoods of the knowledge graph.

PageIndex vs.\ LightRAG is also instructive: PageIndex matches LightRAG accuracy (35.2\% vs.\ 33.9\% Hit@10) with an order of magnitude fewer articles (3.9 vs.\ 32.8), validating hierarchical navigation but exposing its ceiling without semantic search. The knowledge model $\mathcal{M}$, separating terminological ($\mathcal{O}$), assertional ($\mathcal{G}$), and structural ($\mathcal{T}$) representations, provides the scaffolding for integrating both approaches.

\section{Conclusion}
\label{sec:conclusion}

This paper introduced a three-tier knowledge graph RAG system for Vietnamese legal QA, built on a formal knowledge model $\mathcal{M} = (\mathcal{O}, \mathcal{G}, \mathcal{T}, \Phi)$ that extends Legal-Onto by separating terminological, assertional, and structural representations. On 375 real questions the system reaches 75.2\% Hit@10 (MRR 0.545), improving over the strongest baseline by 41.3pp. The central finding is that structural navigation and semantic graph retrieval are complementary: neither alone exceeds 62\%, but their fusion reaches 75\%.

\textbf{Limitations.} Tier~1 tree traversal requires multiple LLM calls, adding $\sim$7\,s of latency per query. Entity extraction has not been validated against a gold-standard annotation. All experiments use Enterprise Law; generalization to other legal domains (e.g., criminal, labor) remains untested.

\textbf{Future work.} We plan to extend the knowledge graph to Investment, Tax, and Labor law, add multi-turn conversational support, investigate reasoning chains beyond two hops, and produce explainable retrieval traces that cite the graph paths used in ranking.

% References ordered by first citation appearance (Vancouver/NLM style)
\begin{thebibliography}{28}
\setlength{\itemsep}{0pt}\setlength{\parsep}{0pt}\setlength{\parskip}{0pt}

\bibitem{r1}
Lewis P, Perez E, Piktus A, et al. Retrieval-Augmented Generation for Knowledge-Intensive NLP Tasks. In: Advances in Neural Information Processing Systems 33 (NeurIPS 2020); 2020. p. 9459-74.

\bibitem{r2}
Reimers N, Gurevych I. Sentence-BERT: Sentence Embeddings using Siamese BERT-Networks. In: Proceedings of the 2019 Conference on Empirical Methods in Natural Language Processing (EMNLP); 2019 Nov 3-7; Hong Kong. 2019. p. 3982-92, doi: 10.18653/v1/D19-1410.

\bibitem{r3}
Gao Y, Xiong Y, Gao X, et al. Retrieval-Augmented Generation for Large Language Models: A Survey. arXiv preprint. 2024. arXiv:2312.10997, doi: 10.48550/arXiv.2312.10997.

\bibitem{r4}
Fan W, Ding Y, Ning L, et al. A Survey on RAG Meeting LLMs: Towards Retrieval-Augmented Large Language Models. In: Proceedings of the 30th ACM SIGKDD Conference on Knowledge Discovery and Data Mining (KDD 2024); 2024. p. 6491-501, doi: 10.1145/3637528.3671470.

\bibitem{r5}
Guo Z, et al. LightRAG: Simple and Fast Retrieval-Augmented Generation. arXiv preprint. 2024. arXiv:2410.05779, doi: 10.48550/arXiv.2410.05779.

\bibitem{r6}
Edge D, Trinh H, Cheng N, et al. From Local to Global: A Graph RAG Approach to Query-Focused Summarization. arXiv preprint. 2024. arXiv:2404.16130, doi: 10.48550/arXiv.2404.16130.

\bibitem{r7}
Zhang M, Tang Y, et al. PageIndex: Next-Generation Vectorless, Reasoning-based RAG. 2025. Available from: https://pageindex.ai/blog/pageindex-intro.

\bibitem{r8}
Nguyen T, Nguyen H, Pham V, Tran D, Selamat A. Legal-Onto: An Ontology-based Model for Representing the Knowledge of a Legal Document. In: Proceedings of the 17th International Conference on Evaluation of Novel Approaches to Software Engineering (ENASE 2022); 2022. p. 426-34, doi: 10.5220/0011088400003176.

\bibitem{r9}
Sartor G, et al. Approaches to Legal Ontologies: Theories, Domains, Methodologies. Dordrecht: Springer; 2011. 272 p., doi: 10.1007/978-94-007-0120-5.

\bibitem{r10}
Karpukhin V, Oguz B, Min S, et al. Dense Passage Retrieval for Open-Domain Question Answering. In: Proceedings of the 2020 Conference on Empirical Methods in Natural Language Processing (EMNLP); 2020. p. 6769-81, doi: 10.18653/v1/2020.emnlp-main.550.

\bibitem{r11}
Asai A, Wu Z, Wang Y, Sil A, Hajishirzi H. Self-RAG: Learning to Retrieve, Generate, and Critique through Self-Reflection. In: Proceedings of the International Conference on Learning Representations (ICLR 2024); 2024, doi: 10.48550/arXiv.2310.11511.

\bibitem{r12}
Yan SQ, et al. Corrective Retrieval Augmented Generation. arXiv preprint. 2024. arXiv:2401.15884, doi: 10.48550/arXiv.2401.15884.

\bibitem{r13}
Gao L, Ma X, Lin J, Callan J. Precise Zero-Shot Dense Retrieval without Relevance Labels. In: Proceedings of the 61st Annual Meeting of the Association for Computational Linguistics (ACL 2023); 2023. p. 1762-77, doi: 10.18653/v1/2023.acl-long.99.

\bibitem{r14}
Bordes A, Usunier N, Garcia-Duran A, Weston J, Yakhnenko O. Translating Embeddings for Modeling Multi-relational Data. In: Advances in Neural Information Processing Systems 26 (NeurIPS 2013); 2013. p. 2787-95.

\bibitem{r15}
Sun Z, Deng Z-H, Nie J-Y, Tang J. RotatE: Knowledge Graph Embedding by Relational Rotation in Complex Space. In: Proceedings of the International Conference on Learning Representations (ICLR 2019); 2019, doi: 10.48550/arXiv.1902.10197.

\bibitem{r16}
Gleich D. PageRank Beyond the Web. SIAM Rev. 2015;57(3):321-63, doi: 10.1137/140976649.

\bibitem{r17}
Jeh G, Widom J. Scaling Personalized Web Search. In: Proceedings of the 12th International Conference on World Wide Web (WWW 2003); 2003 May 20-24; Budapest, Hungary. New York: ACM; 2003. p. 271-9, doi: 10.1145/775152.775191.

\bibitem{r18}
Robertson S, Zaragoza H. The Probabilistic Relevance Framework: BM25 and Beyond. Found Trends Inf Retr. 2009;3(4):333-89, doi: 10.1561/1500000019.

\bibitem{r19}
Manning C, Raghavan P, Schutze H. Introduction to Information Retrieval. New York: Cambridge University Press; 2008. 544 p., doi: 10.1017/CBO9780511809071.

\bibitem{r20}
Chalkidis I, Fergadiotis M, Malakasiotis P, Aletras N, Androutsopoulos I. LEGAL-BERT: The Muppets Straight out of Law School. In: Findings of the Association for Computational Linguistics: EMNLP 2020; 2020. p. 2898-904, doi: 10.18653/v1/2020.findings-emnlp.261.

\bibitem{r21}
Do N, Nguyen H, Selamat A. Knowledge-Based model of Expert Systems using Rela-model. Int J Softw Eng Knowl Eng. 2018;28(8):1047-90, doi: 10.1142/S0218194018500304.

\bibitem{r22}
Nguyen DQ, Nguyen AT. PhoBERT: Pre-trained Language Models for Vietnamese. In: Findings of the Association for Computational Linguistics: EMNLP 2020; 2020. p. 1037-42, doi: 10.18653/v1/2020.findings-emnlp.92.

\bibitem{r23}
Vu T, Nguyen DQ, Nguyen DQ, Dras M, Johnson M. VnCoreNLP: A Vietnamese Natural Language Processing Toolkit. In: Proceedings of the 2018 Conference of the North American Chapter of the Association for Computational Linguistics: Demonstrations (NAACL 2018); 2018. p. 56-60, doi: 10.18653/v1/N18-5012.

\bibitem{r24}
Ngo H, Nguyen T, Nguyen D, Pham M. AimeLaw at ALQAC 2021: Enriching Neural Network Models with Legal-Domain Knowledge. In: Proceedings of the 13th International Conference on Knowledge and Systems Engineering (KSE 2021). IEEE; 2021, doi: 10.1109/KSE53942.2021.9648712.

\bibitem{r25}
Devlin J, Chang M, Lee K, Toutanova K. BERT: Pre-training of Deep Bidirectional Transformers for Language Understanding. In: Proceedings of the 2019 Conference of the North American Chapter of the Association for Computational Linguistics: Human Language Technologies (NAACL-HLT 2019); 2019. p. 4171-86, doi: 10.18653/v1/N19-1423.

\bibitem{r26}
Zhong H, Xiao C, Tu C, Zhang T, Liu Z, Sun M. How Does NLP Benefit Legal System: A Summary of Legal Artificial Intelligence. In: Proceedings of the 58th Annual Meeting of the Association for Computational Linguistics (ACL 2020); 2020. p. 5218-30, doi: 10.18653/v1/2020.acl-main.466.

\bibitem{r27}
Cui J, Li X, Shao Z, et al. A Survey on Legal Large Language Models. arXiv preprint. 2024. arXiv:2312.03718, doi: 10.48550/arXiv.2312.03718.

\bibitem{r28}
Cormack GV, Clarke CLA, Buettcher S. Reciprocal Rank Fusion Outperforms Condorcet and Individual Rank Learning Methods. In: Proceedings of the 32nd International ACM SIGIR Conference on Research and Development in Information Retrieval (SIGIR 2009); 2009. p. 758-9, doi: 10.1145/1571941.1572114.

\end{thebibliography}

\end{document}
